Repeat Yourself? When Linux kernel maintainers balance Code Duplication and Readability

### 2025-10-24 paper/techdebt2026/techdebt.tex
Shorten refactoring method description
Replace details about refactoring methods used with a brief comment,
as this is not relevant to this paper.

Regarding to refactor methods ....

%TODO: nao descrever e discutir mais as estrategias de refatoracao por patch ...
Seven groups applied the parameterized refactor method, two groups used the extractor method, and one group applied the inline method to their approaches to mitigate their duplications. Four patches do not contain a refactoring technique defined in the literature (undefined). Six groups had their patches accepted and fully merged into Linux; four groups had their patches dropped; one group has its patchset partially applied and is still working on patch submission, currently in the sixth version of the patch when this document was written, but we can also consider this case as accepted.

>>>>

We observed that most groups applied the parameterized refactor method while a few used the extractor method.
